---
title: "Awesome stuff"
author: "Dr Tom August"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

Use this example R script to practice compiling an R Markdown file, using the tutorial materials provided at: ourcodingclub.github.io/2016/11/24/rmarkdown-1.html

Follow through the tutorial to make a well commented, easy to follow record of what is going on so that others can easily follow.

```{r, message=FALSE}
# Loading packages
library(dplyr)
```

# Loading biodiversity data
This data is a publicly available dataset of occurrence records for many animal, plant, and fungi species, for 2000-2016 from the NBN Gateway

```{r}
edidiv <- read.csv("edidiv.csv")

# Constructing a table of species richness in each taxonomic group

richness <- 
  edidiv %>%
  group_by(taxonGroup) %>%
  summarise(Species_richness = n_distinct(taxonName))

richness
```

Now i need to create a bar plot

```{r}
# Creating a barplot of species richness in each taxonomic group

barplot(richness$Species_richness, 
        names.arg = richness$taxonGroup, 
        xlab = "Taxa", ylab = "Number of species", 
        ylim = c(0,600)
) 
```

Bar plot done, that looks okay

```{r}
# Determining what the most common species is in each taxonomic group 

max_abund <-
  edidiv %>%
  group_by(taxonGroup) %>%
  summarise(taxonName = names(which.max(table(taxonName))))

max_abund
```

Okay, got the most common species, now i need to get these together

```{r}
# Joining the two data frames together, using "taxonGroup" as the reference

richness_abund <- inner_join(richness, max_abund, by = "taxonGroup")

# Renaming the headers of the tables, and viewing the data frame

richness_abund <- rename(richness_abund, Most_abundant =  taxonName, Taxon = taxonGroup)

richness_abund
```

Taadaa